---
title: "Variable relevance mesures (glmnet)"
author: "Oriol Rovira"
date: "4/6/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Data from Idealista.com 


The data come from [idealista-data] (https://github.com/seralexger/idealista-data)

Author: Alejandro German (Alex seralexger)

(Douwnloaded March 2nd, 2018)

The R-markdown file `rent_housing_data.Rmd" has been used to read the data and to save some of them into `"rhBM_Price.Rdata"`.

```{r}
load(file="rhBM_Price.Rdata") 
# rhBM.price, rhBM.priceByArea,
names(rhBM.price)
log.size <- TRUE
if (log.size){
  rhBM.price$size <- log(rhBM.price$size)
  names(rhBM.price)[11]<-"log.size"
} 
```

```{r}
names(rhBM.priceByArea)
```

We define training and test set, fit these models, and apply variable relevance measures.

### Training and test sets

```{r}
n <- dim(rhBM.price)[1]
pr.tr <- .7
pr.te <- 1 - pr.tr
n.tr <- round(n*pr.tr)
set.seed(123456)
Itr <- sample(1:n,n.tr)
Ite <- setdiff(1:n,Itr)
n.te <- n-n.tr 
```


```{r}
library(mgcv)
library(MASS)
library(Metrics)
library(caret)
library(dplyr)
library('glmnet')
```


```{r}
fit.glmnet.lasso <- glmnet(as.matrix(rhBM.price[, -1]),
                           as.matrix(rhBM.price[, 1]),
                           alpha = 1)
plot(fit.glmnet.lasso)
```

```{r}
fit.glmnet.ridge <- glmnet(as.matrix(rhBM.price[, -1]),
                           as.matrix(rhBM.price[, 1]),
                           alpha = 0)
plot(fit.glmnet.ridge)
```



```{r}
x_vars <- model.matrix(price~. , rhBM.price)[,-1]
y_var <- rhBM.price$price
x_test = (-Itr)
y_test = y_var[x_test]
 
cv_output <- cv.glmnet(x_vars[Itr,], y_var[Itr],
                       alpha = 1, nfolds = 5)
plot(cv_output) 

#Identifying best lamda
best_lam_lasso <- cv_output$lambda.min

lam.1se_lasso <- cv_output$lambda.1se
lam.1se_lasso
```

```{r}
lasso_best <- glmnet(x_vars[Itr,], y_var[Itr], alpha = 1, lambda = best_lam_lasso)
lasso_1se <- glmnet(x_vars[Itr,], y_var[Itr], alpha = 1, lambda = lam.1se_lasso)
```

```{r}
# Predicting in the test sample
y.hat.te <- as.numeric( predict(lasso_1se , s = lam.1se_lasso, newx = x_vars[x_test,]) )

plot(log(rhBM.price$price[Ite]),y.hat.te,
     main=paste("Corr^2=",round(cor(log(rhBM.price$price[Ite]),y.hat.te)^2,2)))
```


```{r}
x_vars <- model.matrix(price~. , rhBM.price)[,-1]
y_var <- rhBM.price$price
x_test = (-Itr)
y_test = y_var[x_test]
 
cv_output <- cv.glmnet(x_vars[Itr,], y_var[Itr],
                       alpha = 0, nfolds = 5)
plot(cv_output)
 
#Identifying best lamda
best_lam_ridge <- cv_output$lambda.min
lam.1se_ridge <- cv_output$lambda.1se
lam.1se_ridge
```

```{r}
ridge_best <- glmnet(x_vars[Itr,], y_var[Itr], alpha = 0, lambda = best_lam_ridge)
ridge_1se <- glmnet(x_vars[Itr,], y_var[Itr], alpha = 0, lambda = lam.1se_ridge)
```

```{r}
# Predicting in the test sample
y.hat.te <- as.numeric( predict(ridge_1se, s = lam.1se_ridge, newx = x_vars[x_test,]) )

plot(log(rhBM.price$price[Ite]),y.hat.te,
     main=paste("Corr^2=",round(cor(log(rhBM.price$price[Ite]),y.hat.te)^2,2)))
```


### Variable relevance measures

```{r}
library(ggplot2)
library(grid)
library(maptools)# For pointLabel

source("C:/Users/Oriol/Desktop/TFG/Scripts inicials/relev.ghost.var.R")
source("C:/Users/Oriol/Desktop/TFG/Scripts inicials/relev.rand.perm.R")
```

## Variable relevance matrix by ghost variables

```{r, fig.height=14, fig.width=14}
relev.ghost.out <- relev.ghost.var(model = lasso_1se, 
                             newdata = rhBM.price[Ite,],
                             func.model.ghost.var= lm)
```


```{r final.graf.Gh, fig.height=14, fig.width=14}
# Plotting only eigenvectors with more than 1% of total relevance
y.hat = predict(lasso_1se, newx = x_vars[Itr,])
sigma2.res = mean((y.hat - y_var[Itr])^2)
plot.relev.ghost.var(relev.ghost.out, n1=n.tr, resid.var=sigma2.res,
                                 vars=1:10, sum.lm.tr=NULL,
                                 alpha=.01, ncols.plot=4)
```

```{r final.graf.Gh.pdf, eval=FALSE}
y.hat = predict(lasso_1se, newx = x_vars[Itr,])
sigma2.res = mean((y.hat - y_var[Itr])^2)
pdf(file="newVarRlevIdealista_glmnet_Lasso_Gh.pdf", height=16, width=12)
# Plotting only eigenvectors with more than 1% of total relevance
plot.relev.ghost.var(relev.ghost.out, n1=n.tr, resid.var=sigma2.res,
                                 vars=1:9, sum.lm.tr=NULL,
                                 alpha=.01, ncols.plot=3)
dev.off()
```

```{r, fig.height=14, fig.width=14}
relev.ghost.out <- relev.ghost.var(model = ridge_1se, 
                             newdata = rhBM.price[Ite,],
                             func.model.ghost.var= lm)
```


```{r final.graf.Gh, fig.height=14, fig.width=14}
# Plotting only eigenvectors with more than 1% of total relevance
y.hat = predict(ridge_1se, newx = x_vars[Itr,])
sigma2.res = mean((y.hat - y_var[Itr])^2)
plot.relev.ghost.var(relev.ghost.out, n1=n.tr, resid.var=sigma2.res,
                                 vars=1:9, sum.lm.tr=NULL,
                                 alpha=.01, ncols.plot=4)
```

```{r final.graf.Gh.pdf, eval=FALSE}
y.hat = predict(ridge_1se, newx = x_vars[Itr,])
sigma2.res = mean((y.hat - y_var[Itr])^2)
pdf(file="newVarRlevIdealista_glmnet_Ridge_Gh.pdf", height=16, width=12)
# Plotting only eigenvectors with more than 1% of total relevance
plot.relev.ghost.var(relev.ghost.out, n1=n.tr, resid.var=sigma2.res,
                                 vars=1:9, sum.lm.tr=NULL,
                                 alpha=.01, ncols.plot=3)
dev.off()
```
## Variable relevance matrix by random permutation

```{r}
relev.rand.out <- relev.rand.perm(model=lasso_1se, 
                              newdata = rhBM.price[Ite,])
```

```{r, fig.height=14, fig.width=14}
# Plotting only eigenvectors with more than 1% of total relevance
plot.relev.rand.perm(relev.rand.out, relev.ghost=relev.ghost.out$relev.ghost,
                                 vars=1:2, sum.lm.tr=NULL,
                                 alpha=.01, ncols.plot=4)
```

```{r final.graf.RP.pdf, eval=FALSE}
pdf(file="newVarRlevIdealista_glmnet_Lasso_RP.pdf", height=16, width=12)
# Plotting only eigenvectors with more than 1% of total relevance
plot.relev.rand.perm(relev.rand.out, relev.ghost=relev.ghost.out$relev.ghost,
                                 vars=1:2, sum.lm.tr=NULL,
                                 alpha=.01, ncols.plot=3)
dev.off()
```

```{r}
relev.rand.out <- relev.rand.perm(model=ridge_1se, 
                              newdata = rhBM.price[Ite,])
```

```{r, fig.height=14, fig.width=14}
# Plotting only eigenvectors with more than 1% of total relevance
plot.relev.rand.perm(relev.rand.out, relev.ghost=relev.ghost.out$relev.ghost,
                                 vars=1:10, sum.lm.tr=NULL,
                                 alpha=.01, ncols.plot=4)
```

```{r final.graf.RP.pdf, eval=FALSE}
pdf(file="newVarRlevIdealista_glmnet_Ridge_RP.pdf", height=16, width=12)
# Plotting only eigenvectors with more than 1% of total relevance
plot.relev.rand.perm(relev.rand.out, relev.ghost=relev.ghost.out$relev.ghost,
                                 vars=1:8, sum.lm.tr=NULL,
                                 alpha=.01, ncols.plot=3)
dev.off()
```