---
title: "Variable relevance mesures (rpart)"
author: "Oriol Rovira"
date: "4/6/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Data from Idealista.com 


The data come from [idealista-data] (https://github.com/seralexger/idealista-data)

Author: Alejandro German (Alex seralexger)

(Douwnloaded March 2nd, 2018)

The R-markdown file `rent_housing_data.Rmd" has been used to read the data and to save some of them into `"rhBM_Price.Rdata"`.

```{r}
load(file="rhBM_Price.Rdata") 
# rhBM.price, rhBM.priceByArea,
names(rhBM.price)
log.size <- TRUE
if (log.size){
  rhBM.price$size <- log(rhBM.price$size)
  names(rhBM.price)[11]<-"log.size"
} 
```

```{r}
names(rhBM.priceByArea)
```

We define training and test set, fit these models, and apply variable relevance measures.

### Training and test sets

```{r}
n <- dim(rhBM.price)[1]
pr.tr <- .7
pr.te <- 1 - pr.tr
n.tr <- round(n*pr.tr)
set.seed(123456)
Itr <- sample(1:n,n.tr)
Ite <- setdiff(1:n,Itr)
n.te <- n-n.tr 
```

```{r}
library(rpart)
library(rpart.plot)
library(mgcv)
```


```{r}
tree<- rpart(formula = log(price) ~ ., data = rhBM.price[Itr,])
```

```{r}
rpart.plot(tree)
```


```{r}
# Predicting in the test sample
y.hat.te <- as.numeric(predict(tree, newdata = rhBM.price[Ite,], type = "vector"))

plot(log(rhBM.price$price[Ite]),y.hat.te,
     main=paste("Corr^2=",round(cor(log(rhBM.price$price[Ite]),y.hat.te)^2,2)))
```

### Variable relevance measures

```{r}
library(mgcv)
library(ggplot2)
library(grid)
library(maptools)# For pointLabel

source("F:/TFG/Scripts inicials/relev.ghost.var.R")
source("F:/TFG/Scripts inicials/relev.rand.perm.R")
```

## Variable relevance matrix by ghost variables

```{r, fig.height=14, fig.width=14}
relev.ghost.out <- relev.ghost.var(model=tree, 
                             newdata = rhBM.price[Ite,],
                             func.model.ghost.var= lm)
```



```{r final.graf.Gh, fig.height=14, fig.width=14}
res.var.tree <- mean(residuals(tree)^2)
# Plotting only eigenvectors with more than 1% of total relevance
plot.relev.ghost.var(relev.ghost.out, n1=n.tr, resid.var=res.var.tree,
                                 vars=1:8, sum.lm.tr=NULL,
                                 alpha=.01, ncols.plot=4)
```

```{r final.graf.Gh.pdf, eval=FALSE}
res.var.tree <- mean(residuals(tree)^2)
pdf(file="newVarRlevIdealista_rpart_Gh.pdf", height=16, width=12)
# Plotting only eigenvectors with more than 1% of total relevance
plot.relev.ghost.var(relev.ghost.out, n1=n.tr, resid.var=res.var.tree,
                                 vars=1:2, sum.lm.tr=NULL,
                                 alpha=.01, ncols.plot=3)
dev.off()
```

## Variable relevance matrix by random permutation

```{r}
relev.rand.out <- relev.rand.perm(model=tree, 
                              newdata = rhBM.price[Ite,])
```

```{r, fig.height=14, fig.width=14}
# Plotting only eigenvectors with more than 1% of total relevance
plot.relev.rand.perm(relev.rand.out, relev.ghost=relev.ghost.out$relev.ghost,
                                 vars=1:8, sum.lm.tr=NULL,
                                 alpha=.01, ncols.plot=4)
```

```{r final.graf.RP.pdf, eval=FALSE}
pdf(file="newVarRlevIdealista_rpart_RP.pdf", height=16, width=12)
# Plotting only eigenvectors with more than 1% of total relevance
plot.relev.rand.perm(relev.rand.out, relev.ghost=relev.ghost.out$relev.ghost,
                                 vars=1:2, sum.lm.tr=NULL,
                                 alpha=.01, ncols.plot=3)
dev.off()
```
